Duplicate Question Detection using Online Learning

### 2016-11-23 paper/main.tex
update paper

\documentclass[journal]{IEEEtran}
%\documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran}

@@

The image below shows the variable importance for the various text features for our Stack overflow model.

\includegraphics[width=\textwidth]{so_varimp.png}

The image below shows the variable importance for the various text features for our Reddit model.

\includegraphics[width=\textwidth]{reddit_varimp.png}

>>>>

%\documentclass[journal]{IEEEtran}
\documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran}

@@

\begin{figure}[ht]
\caption{Variable importance for the various text features for our Stack overflow model}
\centering
\includegraphics[width=0.4\textwidth]{so_varimp.png}
\end{figure}

\begin{figure}[ht]
\caption{Variable importance for the various text features for our Reddit model}
\centering
\includegraphics[width=0.4\textwidth]{reddit_varimp.png}
\end{figure}
